Figure 4

### 2023-07-24 Figures/Figure4.Rmd
minor fix dplyr Figure4.Rmd

prepare_table <- function(correlations, pvalues) {
  correlations %<>% select(...1, order(.[9, -1], decreasing = T))
  pvalues %<>% dplyr::select(colnames(correlations))

>>>>

prepare_table <- function(correlations, pvalues) {
  order <- pivot_longer(correlations, -`...1`) %>%
    dplyr::filter(`...1` == "Mean") %>%
    dplyr::arrange(desc(value)) %>%
    .$name

    correlations %<>% dplyr::select(...1, all_of(order))
    pvalues %<>% dplyr::select(...1, all_of(order))
